Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
added figure about completeness threshold
reviewed Illustrative Example for CT

\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
\missingfigure{picture for completeness threshold}

@@

We illustrate our approach with \todo{what example is this?} example,
extracted from the literature~\cite{?}.
%% Next, we demonstrate how our approach solves the synthesis problem for this
%% example.

@@

In the subsequent iteration, the synthesiser can't find any more
candidates and returns UNSAT, meaning that the current precision is
insufficient.  Consequently, we increase the precision to $I_p=17$,
$F_p=7$.
%
Since the previous counterexamples were obtained at lower precision,
we remove them from the set of counterexamples.  Back in the {\sc
  synthesize} phase, we re-start the process with a candidate solution
with all coefficients $0$.  Next, the {\sc safety} verification stage
provides the first counterexample at higher precision, $x_0=[-0.5
  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
However, this candidate triggers the counterexample
$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
stage.  In the next iteration, we get the candidate $K=[0 \ 0
  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
  \ 0.5]$. Finally, {\sc synthesize} find the candidate $K=[0.01171875
  \ -0.013671875 \ -0.013671875]$, which is validated as a final
solution by all the verification stages.

>>>>

%\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
%\missingfigure{picture for completeness threshold}

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold}
\end{figure*}

@@

We illustrate our approach with \todo{what example is this?} example,
extracted from the literature~\cite{Franklin15}.
%% Next, we demonstrate how our approach solves the synthesis problem for this
%% example.

@@

In the subsequent iteration, the synthesiser is unable to find further 
suitbale candidates and it returns UNSAT, meaning that the current precision is
insufficient.  Consequently, we increase the precision to $I_p=17$,
$F_p=7$.
%
Since the previous counterexamples were obtained at lower precision,
we remove them from the set of counterexamples.  Back in the {\sc
  synthesize} phase, we re-start the process with a candidate solution
with all coefficients $0$.  Next, the {\sc safety} verification stage
provides the first counterexample at higher precision, $x_0=[-0.5
  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
However, this candidate triggers the counterexample
$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
stage.  In the next iteration, we get the candidate $K=[0 \ 0
  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
  \ -0.013671875 \ -0.013671875]$, which is validated as a final
solution by all verification stages.
